NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-28 paper/application.tex
update evaluation

\begin{figure}[htbp]
\centering
%\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{predictStability}
 \caption{
Prediction stability assessment. In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples). The user can drill down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a case by case exploration, as illustrated in (d)(e). For highly unstable outliers, we often observe the prediction of the original sentences near the decision boundary (e.g., the yellow circle in (f) corresponds to a entailment prediction that is very close to neural), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``heap'' is replace by ``pile'' in the hypothesis sentence).
%
}
\label{fig:predictStability}
\end{figure}

@@

By viewing the distribution of the stability in the histogram (Fig.~\ref{fig:predictStability}(a)(b)(c)), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
%
We can observe a drastic difference between the stability for entailment predictions compare to the contradiction and neutral ones.
%
Such a distinction can be partially explained by how entailment relationship is defined. As discussed in the Section~\ref{sec:background}, the relationship is only valid if the concept in premise is more specific than the concept in hypothesis (therefore, you can infer the hypothesis from the premise, but not other way around). This means, we may change the entailment relationships simply by replacing nouns and verb by synonymous, whereas, the same does not apply for neutral and contradiction.
%
By exploring the inherent sensitivity difference among the three types of relationship, the researcher may consider designing dedicate model mechanism to address the such a disparity.

@@

\subsection{Scenario 2: Examine the Decision Making Process}

@@

\begin{itemize}
\item A very young child in a red plaid coat and pink winter hat makes a snowball in a large pile of snow .
\item A child in a red plaid coat and pink winter hat makes a snowball in a large heap of snow .
\end{itemize}

%Hypothesizing
Interpreting how the model arrive at a prediction is one of the most important goal for the expert driven exploratory analysis.
%

 first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
%
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.

@@

%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason
Does the model arrived at the correct prediction for the wrong reason?

\subsection{Scenario 3: What Does It Take to Correct a Wrong Prediction?}
In the previous section, we discussed how we can use forward prediction

\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
Can attention capture grammar structure? Is

\subsection{Scenario 5: Handcraft Example Analysis}
To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:background}) that they know most model will have a difficult time making correct inference. 
%
%The exploration is just started once the prediction result is examined, 
Often the researchers have a set of "what if..." experiments they would like to run. And dependent on the experiment out come, they like will have new questions to ask and try out the different variations or combinations.
%
In some way, we can think of such a process as a nature blend of all previously discussed scenario, where the domain experts do not necessarily have specific goal in mind, instead focus on probing around and see if they can find anything interesting and out-of-ordinary behaviors in the model.
%
Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures an streamlined exploration experience that free the users from interruption and grunt work, allow them to focus on more productive activity.

>>>>

\begin{figure}[htbp]
\centering
%\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{predictStability}
 \caption{
Prediction stability assessment. In (a)(b)(c), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples). The user can drill down to individual examples by filtering via the histogram and scatterplot (see Fig.~\ref{fig:summaryView}) for a case by case exploration, as illustrated in (d)(e). For highly unstable outliers, we often observe the prediction of the original sentences near the decision boundary (e.g., the yellow circle in (f) corresponds to a entailment prediction that is very close to neural), however, some predictions, such as the one illustrated in (d) can alter the prediction quite drastically with minor perturbation (illustrated in $d_1$, where the word ``pile'' is replace by ``heap'' in the hypothesis sentence).
%
}
\label{fig:predictStability}
\end{figure}

@@

By viewing the distribution of the stability in the histogram (Fig.~\ref{fig:predictStability}(a)(b)(c)), we estimate the overall prediction stability (regarding synonymous perturbation) for each type prediction over the entire development set (10k examples).
%
We can observe a drastic difference between the stability for entailment predictions compare to the contradiction and neutral ones.
%
Such a distinction can be partially explained by how entailment relationship is defined. As discussed in the Section~\ref{sec:languageInference}, the relationship is only valid if the concept in premise is more specific than the concept in hypothesis (therefore, you can infer the hypothesis from the premise, but not other way around). This means, we may change the entailment relationships simply by replacing nouns and verb by synonymous, whereas, the same does not apply for neutral and contradiction.
%
By exploring the inherent sensitivity difference among the three types of relationship, the researcher may consider designing dedicate model mechanism to address the such a disparity.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% perturb input, attention
\subsection{Scenario 2: Examine the Decision Making Process}

@@

%Hypothesizing
Examining how the model arrive at a prediction is not only instrumental for evaluating the model performance but also essential for hypothesizing improvement strategies.
%
A model may produce the correct prediction for the wrong reason (or the randomness of ), the prediction may be correct due to luc label provide one way to evaluation model. To ensure a model does what it intended to do, we need to answer the questions whether the model arrived at the correct prediction for the wrong reason? prediction can mean a number of things
It is not only the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.

The three stages (encoder, attention, classifier) work in synergy to produce the prediction.
%
Therefore, making sense of the prediction involving understand how different part of the model affect the final prediction.
%

The example discussed in the previous section, 
\textbf{P}: ``A very young child in a red plaid coat and pink winter hat makes a snowball in a large \emph{pile} of snow.''
\textbf{H}: ``A child in a red plaid coat and pink winter hat makes a snowball in a large \emph{heap} of snow.''

@@

%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 3: What Does It Take to Correct a Wrong Prediction?}
Once, we get a sense of how prediction are being made, where it went wrong. The next obvious questions are what does it take to correct the wrong prediction. 
In addition, when we interpreting how decision are made, we always fix the model and make forward pass in the neural network.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
There is no simple answer to what exactly is the information attention captures.
Can attention capture grammar structure? Is

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 5: Handcraft Example Analysis}
To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most model will have a difficult time making correct inference. 
%
%The exploration is just started once the prediction result is examined, 
Often the researchers have a set of "what if..." experiments they would like to run. And dependent on the experiment out come, they like will have new questions to ask and try out the different variations or combinations.
%
In some way, we can think of such a process as a nature blend of all previously discussed scenario, where the domain experts do not necessarily have specific goal in mind, instead focus on probing around and see if they can find anything interesting and out-of-ordinary behaviors in the model.
%
Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures an streamlined exploration experience that free the users from interruption and grunt work, allow them to focus on more productive activity.
